### 2025-03-31 decision-making.qmd
20250331 - bracketing

@@

@@

As demonstrated from these examples, when the crowd-averaged predictions are centered on the truth, the crowd-averaged predictions are perfectly accurate and are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).
When the crowd-averaged predictions bracket but are not centered on the truth, the crowd-averaged predictions are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).
When the crowd-averaged predictions do not bracket the truth, the crowd-averaged predictions are as accurate as the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).

@@

### Does Fantasy Football Luck or Skill? {#sec-luckOrSkill}

>>>>

As demonstrated above, when the crowd-averaged predictions are centered on the truth, the crowd-averaged predictions are perfectly accurate and are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).

@@

As demonstrated above, when the crowd-averaged predictions bracket but are not centered on the truth, the crowd-averaged predictions are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).

Here is another code example of when the crowd-averaged predictions bracket but are not centered on the truth for a player:

```{r}
predictedValues <- c(10,29,29,40,60,70,80,90)
actualValue <- 15
errors <- predictedValues - actualValue

As demonstrated above, when the crowd-averaged predictions bracket but are not centered on the truth, the crowd-averaged predictions are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError), but they can still be less accurate than the individual forecaster who is at the 50th percentile in accuracy.

@@

As demonstrated above, when the crowd-averaged predictions do not bracket the truth, the crowd-averaged predictions are as accurate as the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).

Here is another code example of when the crowd-averaged predictions do not bracket the truth for a player:

```{r}
predictedValues <- c(0,65,70,75,80,85,90,95)
actualValue <- 100
errors <- predictedValues - actualValue

As demonstrated above, when the crowd-averaged predictions do not bracket the truth, the crowd-averaged predictions are as accurate as the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError), but they can be less accurate than the individual forecaster who is at the 50th percentile in accuracy.

In conclusion, as demonstrated from these examples, when the crowd-averaged predictions are centered on the truth, the crowd-averaged predictions are perfectly accurate and are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError).
When the crowd-averaged predictions bracket but are not centered on the truth, the crowd-averaged predictions are more accurate than the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError), but they can still be less accurate than the individual forecaster who is at the 50th percentile in accuracy.
When the crowd-averaged predictions do not bracket the truth, the crowd-averaged predictions are as accurate as the accuracy of the typical individual forecaster in terms of [mean absolute error](#sec-meanAbsoluteError), but they can be less accurate than the individual forecaster who is at the 50th percentile in accuracy.

In sum, going with crowd-averaged projections will always yield predictions that are as or more accurate (in terms of [mean absolute error](#sec-meanAbsoluteError)) than the (collective) accuracy of the individuals' projections.
However, the crowd-averaged projections may be less accurate than any individual projection, including the projection of the forecaster who is at the 50th percentile in accuracy.
That is, depending on the bracketing rate, the crowd-averaged projections can still be less accurate than most individual projections.

@@

### Is Fantasy Football a Game of Luck or Skill? {#sec-luckOrSkill}
